--- 
title: "Data Analysis Note"
subtitle: "Exploratory Data Analysis & Visualization with R"
author: "Manboha"
date: "`r Sys.Date()`"
documentclass: krantz
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
lot: no
lof: no
graphics: yes
urlcolor: blue
geometry: "left=1.5in, right=1.5in, top=1.25in, bottom=1.25in"
description: This note is a collection of resources designed to help to study exploratory data analysis and visualization with R.
#documentclass: book
#classoption: openany
site: bookdown::bookdown_site
always_allow_html: yes  
---
```{r include=FALSE, cache=FALSE}
## Adapted from Rafael A. Irizarry's Introduction to Data Science
rm(list = ls(all = TRUE))
library(maps)  # load maps first to avoid map conflict with purrr
library(MASS)  # load MASS and matrixStats first to avoid select and count conflict
library(matrixStats) 
library(tidyverse)

# Adapted from Hadley Wickham and Garrett Grolemund's r4ds
options(digits = 3, width = 72, formatR.indent = 2)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  width = 72,
  tidy.opts=list(width.cutoff=72, tidy=TRUE),
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.height = 3.708,  # width * 1 / phi
  fig.show = "hold")

options(dplyr.print_min = 5, dplyr.print_max = 5)

```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'), 'packages.bib')
```

# Preface {-}

This note is a collection of resources designed to help to study exploratory data analysis and visualization with R.

This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International [CC BY-NC-SA 4.0](https://creativecommons.org/licenses/by-nc-sa/4.0).


# Acknowledgments {-}

Many thanks to all the people involved in developing and maintaining R base, the tidyverse, and the other package used for this note.

A special thanks to Rafael A. Irizarry, Pablo Casas, Zach Bogart, Joyce Robbins, Rob Kabacoff from whom I inspired ideas. 
Rafael A. Irizarry is author of "Introduction to Data Science". 
Pablo Casas is author of "Data Science Live Book".
Zach Bogart and Joyce Robbins is author of "edav.info/".
Rob Kabacoff is author of "Data Visualization with R".

 


<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
## Adapted from Rafael A. Irizarry's Introduction to Data Science
rm(list = ls(all = TRUE))
library(maps)  # load maps first to avoid map conflict with purrr
library(MASS)  # load MASS and matrixStats first to avoid select and count conflict
library(matrixStats) 
library(tidyverse)

# Adapted from Hadley Wickham and Garrett Grolemund's r4ds
options(digits = 3, width = 72, formatR.indent = 2)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  width = 72,
  tidy.opts=list(width.cutoff=72, tidy=TRUE),
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.height = 3.708,  # width * 1 / phi
  fig.show = "hold")

options(dplyr.print_min = 5, dplyr.print_max = 5)

```
# Introduction {-}



<!--chapter:end:intro.Rmd-->

